\documentclass[10pt]{article}
\setlength{\textwidth}{6.3in}
\setlength{\textheight}{9in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\topmargin}{-.5in}
%\parindent=0in
\linespread{1.3}
\usepackage{ mathrsfs }
\usepackage{amsthm}
\usepackage{ amssymb }
\usepackage{graphicx}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[]{Lemma}
\newtheorem{definition}[]{Definition}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\usepackage{nicematrix}

\pagestyle{fancy}
\headheight = 14.5pt
\lhead{HW1, Thomas Zeng }
\rhead{Stat 250, Spring 2023}
\cfoot{\thepage}


\begin{document}
\noindent
\textbf{Time taken: $0.5$ hours}

\section*{1}

\subsection*{(a)}
The population is all high school students. The sample is $1500$ high school students. The $47\%$ is a statistic.

\subsection*{(b)}
The population is everyone in the United States. The $9.6\%$ is a parameter.

\subsection*{(c)}
The population is all NBA players. The height is a parameter.

\subsection*{(d)}
The population is US adults. The sample is 2106 adults. The $19\%$ is a statistic.

\section*{2}
\subsection*{(a)}
The population parameter of interest is the mean weight of trout in a lake.
\subsection*{(b)}
All $12$ trout is captured from one specific location of the lake. If the weight of trout defer depending on location in lake, then this sample would not be a representative sample.

\section*{3}

\subsection*{(a)}
The treatments are either play Tetris for at least 10 minutes or fill out a log detailing their activies.

\subsection*{(b)}
No, as the patient clearly will know the treatment that they were asigned.

\subsection*{(c)}
Yes, as the treatments were assigned randomly.

\subsection*{(d)}
No, as the patients were recruited rather than sampled randomly.

\section*{4}

\subsection*{(a)}
This is an observational study.

\subsection*{(b)}
No, as the ``treatments'' were not randomly assigned (since this is an observational study). Therefore, we do not know if there may be cofounding variables.




\end{document}